---
title: "Factor Analysis"
author: "Thales Lima"
date: "06/05/2021"
output: html_document
---

# Measuring Social Values and Preferences for Redistribution
  
## Introduction
  
The goal of this work is to explore a social value measure given by S.H Schwartz
and test it against preferences for redistribution (PR). Inspired by the work of Alesina and Giuliano
(2010) and Heldt *et al* (2009). Following variables from the [World Value Survey 6](https://www.worldvaluessurvey.org/wvs.jsp) we will first use a Factor Analysis approach in order to reduce from 10 Schwartz variables to 3 or 4 and then test it against a PR model. 
  
## Schwartz Social Values
  
Schwartz tries to get a more statistical way of understanding the different universal values in order to try to compare and analyse the differences among cultures. The idea of describing it as a circle arises from the fact that the author wanted to express a dynamic among these values in the sense that there are some values that are complementaries and other ones that are opposites. Just to illustrate, the 10 aspects described at his work are the following: Self-Direction,  Stimulation, Hedonism, Achievement, Power, Security, Conformity, Tradition, Benevolence, Universalism.
  
According to Held et al (2009), each of these values are represented by each one of the 10 questions presented at this version of WVS. However, they found that instead of 4 mais clusters, 3: 
    * Excitement: ( V76, 75, 71, 73, 70)
    * Caretake: (V70, 78, 74B, 79, 74)
    * Security & Conformity: (V79, 77, 72)
  
All of the questions are rated from 1 (very much like me) to 6 (not at all like me): It is important to this person to think up new ideas and be creative; to do things one’s own way (V70), It is important to this person to be rich; to have a lot of money and expensive things (V71), Living in secure surroundings is important to this person; to avoid anything that might be dangerous (V72), It is important to this person to have a good time; to “spoil” oneself (V73), It is important to this person to do something for the good of society (V74), It is important for this people to help the people nearby; to care for their well-being (V74B), Being very successful is important to this person; to have people recognize one’s achievements (V75), Adventure and taking risks are important to this person; to have an exciting life (V76), It is important to this person to always behave properly; to avoid doing anything people would say is wrong (V77), Looking after the environment is important to this person; to care for nature and save life resources (V78) and Tradition is important to this person; to follow the customs handed down by one’s religion or family (V79).
  
## Factor Analysis   
  
We will use a package named [Psych](https://cran.r-project.org/web/packages/psych/index.html):
  
```{r pacotes}
library(psych)
```
  
```{r include = FALSE} 
library(openxlsx)
base <- read.xlsx(xlsxFile = "C:/Users/Thalles/Documents/Preferences for Redistribution/Bases/Recoded data - 12-08.xlsx")
```
  
We will now start an explanatory factor analysis, starting with a useful plot named `` `scree` ``, this plot  indicates the number of factors (black dots) and components (white dots) taken from their respective eigenvalues that are bigger than one. Eigenvalues smaller than one indicate that the original variable carries more information then the combined one, it is plausible to conclude that it is better to use the unchanged variable.    

``` {r scree}
scree(base[c(8:18)])
```

  

